Stressing Bank Profitability for Interest Rate Risk$^*$ \\ \vspace{0.5cm} Preliminary and Incomplete \vspace{0.5cm}

### 2013-09-05 LATEX/workplan.aug.18.tex
Workplan explaining Rossi et al (2013) and PLS paper Slides in progress for Atlanta

\begin{enumerate}
\item No change forecast 
\begin{itemize}
\item I'm listing this first because I think the tables should only report RMSEs for the no change forecast and show all other RMSE's as relative to the no change forecast's RMSE.  
\item It may also be worth having a table reporting Barbara's full sample $A$ measures, just to set things up for later.  From an ordering perspective they should be the same as reporting relative RMSEs.  That is, while relative RMSEs are $\sqrt{\sum \epsilon^{2}_{alt.mod.}}/\sqrt{\sum \epsilon^{2}_{no.chg}}$, Barbara's $A$ measure is  $\sum \epsilon^{2}_{alt.mod.}-\sum \epsilon^{2}_{no.chg}$.
\item Additionally, it may also be work having some charts reporting rolling window relative RMSEs and rolling window versions of Barbara's $A$ measure.  
\begin{itemize}
\item It would probably make sense to do this only for a selection of models (i.e., models that are different enough).  
\item Doing the rolling window versions of Barbara's $A$ measure would set things up later for doing the hand-wavy version of Barbara's decomposition. (Recall, that we can not do a proper version of Barbara's decomposition because she does it for DAR forecasts and while we could do DAR forecasts they do not really make sense when we want to do conditional forecasts.)  
\end{itemize}
\end{itemize}
\item Models with yields
\begin{enumerate}
\item Equally-weighted average (EWA) of 12 recursive autoregression (RAR) models that individual includes all 12 yields 
\item EWA of 3 RAR models that individually include the 3-month rate, 2-year yield, and 10-year yield
\item EWA of 2 RAR models that individually include the 3-month rate and 10-year yield
\end{enumerate}
\item Models with data-based factors ($level=10.year.yield$, $slope=10.year.yield–-3.month.rate$, and $curvature=2*2.year.yield–-3.month.rate–-10.year.yield$)
\begin{enumerate}
\item RAR model that jointly includes the 3 data-based factors
\item EWA of 3 RAR models that individually include the 3 data-based factors
\end{enumerate}
\item Models with PCA-based factors (1st PC, 2nd PC, and 3rd PC)
\begin{enumerate}
\item RAR model that jointly includes the first 3 PCA-based factors
\item EWA of 3 RAR models that individually include the first 3 PCA-based factors
\end{enumerate}
\item Models with Nelson-Siegel model-based factors (level, slope, and curvature)
\begin{enumerate}
\item RAR model that jointly includes the 3 Nelson-Siegel-based factors
\item EWA of 3 RAR models that individually include the 3 Nelson-Siegel-based factors
\end{enumerate}
\item Models with PLS-based factors
\begin{enumerate}
\item RAR model that jointly includes the first 3 PLS-based factors
\item EWA of 3 RAR models that individually include the first 3 PLS-based factors
\item RAR model that includes the first PLS-based factor
\end{enumerate}
\item Should we include the system approaches that we have already done
\begin{enumerate}
\item The VAR model with NIMs and the data-based factors
\item The VAR model with NIMs and the Nelson-Siegel model-based factors
\end{enumerate}
\item Bayesian model averaging – should we pursue?
\end{enumerate}

@@

\item Models A and G can be estimated for different step-ahead equations and over fixed rolling windows and used to forecast out-of-sample.  This will imply for every period and every h-step ahead forecast a squared forecast error $\left(\overrightarrow{\eta}^{\alpha}_{t+h}\right)^{2}$ and

@@

\item For one-step ahead we have $\left\{\left(\overrightarrow{\eta}^{\alpha}_{R+i+1|R+i}\right)^{2}\right\}_{i=0}^{T-R-1}$ and $\left\{\left(\overrightarrow{\eta}^{\gamma}_{R+i+1|R+i}\right)^{2}\right\}_{i=0}^{T-R-1}$, where in each case the rolling window estimation period \underline{and data used to generate the forecast}

@@

\item For two-step ahead we have $\left\{\left(\overrightarrow{\eta}^{\alpha}_{R+i+2|R+i}\right)^{2}\right\}_{i=0}^{T-R-2}$ and $\left\{\left(\overrightarrow{\eta}^{\gamma}_{R+i+2||R+i}\right)^{2}\right\}_{i=0}^{T-R-2}$, where in each case the rolling window estimation period \underline{and data used to generate the forecast} ends at $R, R+1, \dots, T-2$.

@@

\item For h-step ahead we have $\left\{\left(\overrightarrow{\eta}^{\alpha}_{R+i+h||R+i}\right)^{2}\right\}_{i=0}^{T-R-h}$ and $\left\{\left(\overrightarrow{\eta}^{\gamma}_{R+i+h||R+i}\right)^{2}\right\}_{i=0}^{T-R-h}$, where in each case the rolling window estimation period \underline{and data used to generate the forecast} ends at $R, R+1, \dots, T-h$.
\item Note there is a different model estimated for each one-step, two-step, ..., h-step ahead forecast and a different model estimated for each date.  

@@

\item For one-step ahead we have $\left\{\overrightarrow{\mathcal{RL}}_{R+i+1|R+i}\right\}_{i=0}^{T-R-1}\!\!\!\!=\left\{\left(\overrightarrow{\eta}^{\alpha}_{R+i+1|R+i}\right)^{2}\!\!-\left(\overrightarrow{\eta}^{\gamma}_{R+i+1|R+i}\right)^{2}\right\}_{i=0}^{T-R-1}$
\item For two-step ahead we have $\left\{\overrightarrow{\mathcal{RL}}_{R+i+2|R+i}\right\}_{i=0}^{T-R-2}\!\!\!\!=\left\{\left(\overrightarrow{\eta}^{\alpha}_{R+i+2|R+i}\right)^{2}\!\!-\left(\overrightarrow{\eta}^{\gamma}_{R+i+2|R+i}\right)^{2}\right\}_{i=0}^{T-R-2}$

@@

\item For h-step ahead we have $\left\{\overrightarrow{\mathcal{RL}}_{R+i+h|R+i}\right\}_{i=0}^{T-R-h}\!\!\!\!=\left\{\left(\overrightarrow{\eta}^{\alpha}_{R+i+h|R+i}\right)^{2}\!\!-\left(\overrightarrow{\eta}^{\gamma}_{R+i+h|R+i}\right)^{2}\right\}_{i=0}^{T-R-h}$

@@

\item So for any date after $R+h$ there are $h$ rolling loss $\overrightarrow{\mathcal{RL}}$ observations, corresponding to different step ahead forecasts.  For date $R+h-1$ there are $h-1$ rolling loss $\overrightarrow{\mathcal{RL}}$ observations, and so on until $R+1$ where there is just one rolling loss $\overrightarrow{\mathcal{RL}}$ observation.
\item Models A and G can be estimated over fixed rolling windows and used to forecast in-sample.  Note that whereas when one forecasts out-of-sample there is for each estimated model only 1 one-step ahead forecast, only 1 two-step ahead forecast, ..., and only 1 h-step ahead forecast, when one forecasts in-sample there is for each fixed rolling window of length $R$, $R-1$ one-step ahead forecasts, $R-2$ two-step ahead forecasts, ..., and $R-h$ h-step ahead forecasts.  When looking at in-sample forecasts errors Barbara only looks at the \emph{very last} one-step, two-step, ..., h-step ahead forecast for that model.  
\item Models A and G estimated over fixed rolling windows and used to forecast in-sample will for every period and every h-step ahead forecast imply a squared forecast error for the last period of the estimation period $\left(\overline{\eta}^{\alpha}_{t}\right)^{2}$ and
 $\left(\overline{\eta}^{\gamma}_{t}\right)^{2}$.  (I'm using ``over arrows'' to denote out-of-sample forecasts.  This is my notation, not Barbara's.)

@@

\item For one-step ahead we have $\left\{\left(\overline{\eta}^{\alpha}_{R+i|R+i-1}\right)^{2}\right\}_{i=0}^{T-R}$ and $\left\{\left(\overline{\eta}^{\gamma}_{R+i|R+i-1}\right)^{2}\right\}_{i=0}^{T-R}$, where in each case the rolling window estimation period

@@

\item For two-step ahead we have $\left\{\left(\overline{\eta}^{\alpha}_{R+i|R+i-2}\right)^{2}\right\}_{i=0}^{T-R}$ and $\left\{\left(\overline{\eta}^{\gamma}_{R+i|R+i-2}\right)^{2}\right\}_{i=0}^{T-R}$, where in each case the rolling window estimation period

@@

\item For h-step ahead we have $\left\{\left(\overline{\eta}^{\alpha}_{R+i|R+i-h}\right)^{2}\right\}_{i=0}^{T-R}$ and $\left\{\left(\overline{\eta}^{\gamma}_{R+i|R+i-h}\right)^{2}\right\}_{i=0}^{T-R}$, where in each case the rolling window estimation period

@@

\item For one-step ahead we have $\left\{\overline{\mathcal{RL}}_{R+i|R+i-1}\right\}_{i=0}^{T-R-1}\!\!\!\!=\left\{\left(\overline{\eta}^{\alpha}_{R+i|R+i-1}\right)^{2}\!\!-\left(\overline{\eta}^{\gamma}_{R+i|R+i-1}\right)^{2}\right\}_{i=0}^{T-R-1}$
\item For two-step ahead we have $\left\{\overline{\mathcal{RL}}_{R+i|R+i-2}\right\}_{i=0}^{T-R-2}\!\!\!\!=\left\{\left(\overline{\eta}^{\alpha}_{R+i|R+i-2}\right)^{2}\!\!-\left(\overline{\eta}^{\gamma}_{R+i|R+i-2}\right)^{2}\right\}_{i=0}^{T-R-2}$

@@

\item For h-step ahead we have $\left\{\overline{\mathcal{RL}}_{R+i|R+i-h}\right\}_{i=0}^{T-R-h}\!\!\!\!=\left\{\left(\overline{\eta}^{\alpha}_{R+i|R+i-h}\right)^{2}\!\!-\left(\overline{\eta}^{\gamma}_{R+i|R+i-h}\right)^{2}\right\}_{i=0}^{T-R-h}$

@@

\item So for the one-step ahead forecast we regress $\left\{\overrightarrow{\mathcal{RL}}_{R+i+1|R+i}\right\}_{i=0}^{T-R-1}$ on $\left\{\overline{\mathcal{RL}}_{R+i|R+i-1}\right\}_{i=0}^{T-R-1}$.  The models being used to generate these losses are estimated one rolling windows that end on $R, R+1, \cdots, T$.
\item So for the two-step ahead forecast we regress $\left\{\overrightarrow{\mathcal{RL}}_{R+i+2|R+i}\right\}_{i=0}^{T-R-1}$ on $\left\{\overline{\mathcal{RL}}_{R+i|R+i-2}\right\}_{i=0}^{T-R-1}$.  The models being used to generate these losses are estimated one rolling windows that end on $R, R+1, \cdots, T$.

@@

\item So for the h-step ahead forecast we regress $\left\{\overrightarrow{\mathcal{RL}}_{R+i+h|R+i}\right\}_{i=0}^{T-R-1}$ on $\left\{\overline{\mathcal{RL}}_{R+i|R+i-h}\right\}_{i=0}^{T-R-1}$.  The models being used to generate these losses are estimated one rolling windows that end on $R, R+1, \cdots, T$.

@@

\item One-step: $\overrightarrow{\mathcal{RL}}_{R+i+1|R+i}=\widehat{\beta}_{1}\overline{\mathcal{RL}}_{R+i|R+i-1}+\widehat{u}_{R+i+1}$, where $i=0, 1, \cdots, T-R-1$.
\item Two-step: $\overrightarrow{\mathcal{RL}}_{R+i+2|R+i}=\widehat{\beta}_{2}\overline{\mathcal{RL}}_{R+i|R+i-2}+\widehat{u}_{R+i+2}$, where $i=0, 1, \cdots, T-R-2$.

@@

\item h-step: $\overrightarrow{\mathcal{RL}}_{R+i+h|R+i}=\widehat{\beta}_{h}\overline{\mathcal{RL}}_{R+i|R+i-h}+\widehat{u}_{R+i+h}$, where $i=0, 1, \cdots, T-R-h$.
\item It may be worth noting that every out-of-sample-based loss being regressed on a corresponding in-sample-based loss uses exactly the same two versions -- where versions refer to the estimation period -- of the A and G model.  That is the models are all estimated on rolling windows ending $R, R+1, \cdots, T$ but the in-sample forecasts use this estimated model but condition on earlier data for period $R-step, R-step+1, \cdots, T-step$ forecasts while the out-of-sample forecasts use this estimated model, condition on $R, R+1, \cdots, T-step$ data and project out  $R+step, R+step+1, \cdots, T+step-step$.

@@

\item One-step: 

@@

\underbrace{\frac{1}{T\!-\!R}\!\!\sum_{i=0}^{T-R-1}\!\!\overrightarrow{\mathcal{RL}}_{R+i+1|R+i}}_{=A_{1,T\!-\!R}}
\!\!\!\!&=&\!\!\!\!\underbrace{\widehat{\beta}_{1}\cdot\frac{1}{T\!-\!R}\!\!\sum_{i=0}^{T-R-1}\!\!\overline{\mathcal{RL}}_{R+i|R+i-1}}_{=B_{1,T\!-\!R}} \nonumber \\
\!\!\!\!&+&\!\!\!\!\underbrace{\frac{1}{T\!-\!R}\!\!\sum_{i=0}^{T-R-1}\!\!\widehat{u}_{R+i+1}}_{=U_{1,T\!-\!R}}, \nonumber

@@

where $i=0, 1, \cdots, T-R-1$.
\item Two-step: 

@@

\underbrace{\frac{1}{T\!-\!R\!-\!1}\!\!\sum_{i=0}^{T-R-2}\!\!\overrightarrow{\mathcal{RL}}_{R+i+2|R+i}}_{=A_{2,T\!-\!R\!-\!1}}
\!\!\!\!&=&\!\!\!\!\underbrace{\widehat{\beta}_{2}\cdot\frac{1}{T\!-\!R\!-\!1}\!\!\sum_{i=0}^{T-R-2}\!\!\overline{\mathcal{RL}}_{R+i|R+i-2}}_{=B_{2,T\!-\!R\!-\!1}} \nonumber \\
\!\!\!\!&+&\!\!\!\!\underbrace{\frac{1}{T\!-\!R\!-\!1}\!\!\sum_{i=0}^{T-R-2}\!\!\widehat{u}_{R+i+2}}_{=U_{2,T\!-\!R\!-\!1}}, \nonumber 

@@

where $i=0, 1, \cdots, T-R-2$.

@@

\item h-step: 

@@

\underbrace{\frac{1}{T\!-\!R\!-\!(h\!-\!1)}\!\!\sum_{i=0}^{T-R-(h-1)}\!\!\overrightarrow{\mathcal{RL}}_{R+i+h|R+i}}_{=A_{h,T\!-\!R\!-\!\!(h\!-\!1)}}
\!\!\!\!&=&\!\!\!\!\underbrace{\widehat{\beta}_{h}\cdot\frac{1}{T\!-\!R\!-\!(h\!-\!1)}\!\!\sum_{i=0}^{T-R-(h-1)}\!\!\overline{\mathcal{RL}}_{R+i|R+i-h}}_{=B_{h,T\!-\!R\!-\!(h\!-\!1)}} \nonumber \\
\!\!\!\!&+&\!\!\!\!\underbrace{\frac{1}{T\!-\!R\!-\!(h\!-\!1)}\!\!\sum_{i=0}^{T-R-(h-1)}\!\!\widehat{u}_{R+i+h}}_{=U_{h,T\!-\!R\!-\!(h\!-\!1)}}, \nonumber

@@

where $i=0, 1, \cdots, T-R-h$.

@@

A_{h,T\!-\!R\!-\!\!(h\!-\!1)}\!\!\!\!&=&\!\!\!\!\frac{1}{T\!-\!R\!-\!(h\!-\!1)}\!\!\sum_{i=0}^{T-R-(h-1)}\!\!\overrightarrow{\mathcal{RL}}_{R+i+h|R+i}. \nonumber

@@

\item For $A_{1,T\!-\!R}$ there are $T-R-m$ possible windows, where the windows are: 
\[\left\{\overrightarrow{\mathcal{RL}}_{R+i+1|R+i}\ \ , \ \  . \ \  . \ \  . \ \ ,\ \ \overrightarrow{\mathcal{RL}}_{R+i+1+m|R+i+m}\right\}_{i=0}^{T-R-1-m}\] 

@@

\[\frac{1}{m}\sum_{j=0}^{m}\overrightarrow{\mathcal{RL}}_{R+i+1+j|R+i+j}\ \ \ \mathrm{for} \ \ \ i=0,1,\cdots,T\!-\!R\!-\!1\!-\!m. \]
\item For $A_{2,T\!-\!R\!-\!1}$ there are $T-R-m-1$ possible windows, where the windows are: 
\[\left\{\overrightarrow{\mathcal{RL}}_{R+i+2|R+i}\ \ , \ \  . \ \  . \ \  . \ \ ,\ \ \overrightarrow{\mathcal{RL}}_{R+i+2+m|R+i+m}\right\}_{i=0}^{T-R-2-m}\] 

@@

\[\frac{1}{m}\sum_{j=0}^{m}\overrightarrow{\mathcal{RL}}_{R+i+2+j|R+i+j}\ \ \ \mathrm{for} \ \ \ i=0,1,\cdots,T\!-\!R\!-\!2\!-\!m. \]

@@

\[\left\{\overrightarrow{\mathcal{RL}}_{R+i+h|R+i}\ \ , \ \  . \ \  . \ \  . \ \ ,\ \ \overrightarrow{\mathcal{RL}}_{R+i+h+m|R+i+m}\right\}_{i=0}^{T-R-h-m}\] 

@@

\[\frac{1}{m}\sum_{j=0}^{m}\overrightarrow{\mathcal{RL}}_{R+i+h+j|R+i+j}\ \ \ \mathrm{for} \ \ \ i=0,1,\cdots,T\!-\!R\!-\!h\!-\!m. \]

@@

>>>>

\begin{enumerate}
\item No change forecast 
\begin{itemize}
\item I'm listing this first because I think we should also show tables of relative RSMEs and for these tables I think the relevant comparison should be relative to the no change forecast.    
\begin{itemize}
\item The first table could show all the RSMEs in absolute terms (as they are now shown).  
\item The second table could show just the RSME for the no change forecast and then relative RSMEs for all other approaches; that is, $\sqrt{\sum \epsilon^{2}_{alt.mod.}}/\sqrt{\sum \epsilon^{2}_{no.chg}}$.
\item The third table could show just the RSME for the no change forecast and then show Barbara's (relative) full sample $A$ measures, defined as $\sum \epsilon^{2}_{alt.mod.}-\sum \epsilon^{2}_{no.chg}$, just to set things up for later. From an ordering perspective Barbara's full sample $A$ measures should be the same as reporting relative RMSEs.
\end{itemize}
\item Additionally, it may also be worth having some charts reporting rolling window relative RMSEs and rolling window versions of Barbara's $A$ measure.  
\begin{itemize}
\item It would probably make sense to do this only for a selection of models (i.e., models that are different enough).  
\item Doing the rolling window versions of Barbara's $A$ measure would set things up later for doing the hand-wavy version of Barbara's decomposition. (Recall, that we can not do a proper version of Barbara's decomposition because she does it for DAR forecasts and while we could do DAR forecasts they do not really make sense when we want to do conditional forecasts.)  
\end{itemize}
\end{itemize}
\item Models with yields
\begin{enumerate}
\item Equally-weighted average (EWA) of 12 recursive autoregression (RAR) models that individual includes all 12 yields 
\item EWA of 3 RAR models that individually include the 3-month rate, 2-year yield, and 10-year yield
\item EWA of 2 RAR models that individually include the 3-month rate and 10-year yield
\end{enumerate}
\item Models with data-based factors ($level=10.year.yield$, $slope=10.year.yield–-3.month.rate$, and $curvature=2*2.year.yield–-3.month.rate–-10.year.yield$)
\begin{enumerate}
\item RAR model that jointly includes the 3 data-based factors
\item EWA of 3 RAR models that individually include the 3 data-based factors
\end{enumerate}
\item Models with PCA-based factors (1st PC, 2nd PC, and 3rd PC)
\begin{enumerate}
\item RAR model that jointly includes the first 3 PCA-based factors
\item EWA of 3 RAR models that individually include the first 3 PCA-based factors
\end{enumerate}
\item Models with Nelson-Siegel model-based factors (level, slope, and curvature)
\begin{enumerate}
\item RAR model that jointly includes the 3 Nelson-Siegel-based factors
\item EWA of 3 RAR models that individually include the 3 Nelson-Siegel-based factors
\end{enumerate}
\item Models with PLS-based factors
\begin{enumerate}
\item RAR model that jointly includes the first 3 PLS-based factors
\item EWA of 3 RAR models that individually include the first 3 PLS-based factors
\item RAR model that includes the first PLS-based factor
\end{enumerate}
\item Should we include the system approaches that we have already done
\begin{enumerate}
\item The VAR model with NIMs and the data-based factors
\item The VAR model with NIMs and the Nelson-Siegel model-based factors
\end{enumerate}
\item Bayesian model averaging – should we pursue?
\end{enumerate}

@@

\item Models A and G can be estimated for different step-ahead equations and over fixed rolling windows and used to forecast out-of-sample.  This will imply for every period and every $h$-step ahead forecast a squared forecast error $\left(\overrightarrow{\eta}^{\alpha}_{t+h}\right)^{2}$ and

@@

\item For $1$-step ahead we have $\left\{\left(\overrightarrow{\eta}^{\alpha}_{R+i+1|R+i}\right)^{2}\right\}_{i=0}^{T-R-1}$ and $\left\{\left(\overrightarrow{\eta}^{\gamma}_{R+i+1|R+i}\right)^{2}\right\}_{i=0}^{T-R-1}$, where the rolling window estimation period \underline{and data used to generate the forecast}

@@

\item For $2$-step ahead we have $\left\{\left(\overrightarrow{\eta}^{\alpha}_{R+i+2|R+i}\right)^{2}\right\}_{i=0}^{T-R-2}$ and $\left\{\left(\overrightarrow{\eta}^{\gamma}_{R+i+2||R+i}\right)^{2}\right\}_{i=0}^{T-R-2}$, where the rolling window estimation period \underline{and data used to generate the forecast} ends at $R, R+1, \dots, T-2$.

@@

\item For $h$-step ahead we have $\left\{\left(\overrightarrow{\eta}^{\alpha}_{R+i+h||R+i}\right)^{2}\right\}_{i=0}^{T-R-h}$ and $\left\{\left(\overrightarrow{\eta}^{\gamma}_{R+i+h||R+i}\right)^{2}\right\}_{i=0}^{T-R-h}$, where the rolling window estimation period \underline{and data used to generate the forecast} ends at $R, R+1, \dots, T-h$.
\item Note there is a different model estimated for each $1$-step, $2$-step, ..., $h$-step ahead forecast and a different model estimated for each date.  

@@

\item For $1$-step ahead: $\left\{\overrightarrow{\mathcal{RL}}_{R+i+1|R+i}\right\}_{i=0}^{T-R-1}\!\!\!\!=\left\{\left(\overrightarrow{\eta}^{\alpha}_{R+i+1|R+i}\right)^{2}\!\!-\left(\overrightarrow{\eta}^{\gamma}_{R+i+1|R+i}\right)^{2}\right\}_{i=0}^{T-R-1}$
\item For $2$-step ahead: $\left\{\overrightarrow{\mathcal{RL}}_{R+i+2|R+i}\right\}_{i=0}^{T-R-2}\!\!\!\!=\left\{\left(\overrightarrow{\eta}^{\alpha}_{R+i+2|R+i}\right)^{2}\!\!-\left(\overrightarrow{\eta}^{\gamma}_{R+i+2|R+i}\right)^{2}\right\}_{i=0}^{T-R-2}$

@@

\item For $h$-step ahead: $\left\{\overrightarrow{\mathcal{RL}}_{R+i+h|R+i}\right\}_{i=0}^{T-R-h}\!\!\!\!=\left\{\left(\overrightarrow{\eta}^{\alpha}_{R+i+h|R+i}\right)^{2}\!\!-\left(\overrightarrow{\eta}^{\gamma}_{R+i+h|R+i}\right)^{2}\right\}_{i=0}^{T-R-h}$

@@

\item So for any date after $R+h$ there are $h$ rolling loss $\overrightarrow{\mathcal{RL}}$ observations, corresponding to different step ahead forecasts, for date $R+h-1$ there are $h-1$ rolling loss $\overrightarrow{\mathcal{RL}}$ observations, for date $R+h-2$ there are $h-2$ rolling loss $\overrightarrow{\mathcal{RL}}$ observations, and so on until $R+1$ where there is just one rolling loss $\overrightarrow{\mathcal{RL}}$ observation.
\item Models A and G can be estimated over fixed rolling windows and used to forecast in-sample.  Note that whereas when one forecasts out-of-sample there is for each estimated model only 1 $1$-step ahead forecast, only 1 $2$-step ahead forecast, ..., and only 1 $h$-step ahead forecast, when one forecasts in-sample there is for each estimated fixed rolling window of length $R$, $R-1$ $1$-step ahead forecasts (for different quarters), $R-2$ $2$-step ahead forecasts (for different quarter), ..., and $R-h$ $h$-step ahead forecasts (for different quarters).  When looking at in-sample forecasts errors Barbara only looks at the \emph{very last} $1$-step, \emph{very last} $2$-step, ..., \emph{very last} $h$-step ahead forecast for that model.  
\item Models A and G estimated over fixed rolling windows and used to forecast in-sample will for every period and every $h$-step ahead forecast imply a squared forecast error for the last period of the estimation period $\left(\overline{\eta}^{\alpha}_{t}\right)^{2}$ and
 $\left(\overline{\eta}^{\gamma}_{t}\right)^{2}$.  (I'm using ``over bars'' to denote in-sample forecasts.  This is my notation, not Barbara's.)

@@

\item For $1$-step ahead we have $\left\{\left(\overline{\eta}^{\alpha}_{R+i|R+i-1}\right)^{2}\right\}_{i=0}^{T-R}$ and $\left\{\left(\overline{\eta}^{\gamma}_{R+i|R+i-1}\right)^{2}\right\}_{i=0}^{T-R}$, where in each case the rolling window estimation period

@@

\item For $2$-step ahead we have $\left\{\left(\overline{\eta}^{\alpha}_{R+i|R+i-2}\right)^{2}\right\}_{i=0}^{T-R}$ and $\left\{\left(\overline{\eta}^{\gamma}_{R+i|R+i-2}\right)^{2}\right\}_{i=0}^{T-R}$, where in each case the rolling window estimation period

@@

\item For $h$-step ahead we have $\left\{\left(\overline{\eta}^{\alpha}_{R+i|R+i-h}\right)^{2}\right\}_{i=0}^{T-R}$ and $\left\{\left(\overline{\eta}^{\gamma}_{R+i|R+i-h}\right)^{2}\right\}_{i=0}^{T-R}$, where in each case the rolling window estimation period

@@

\item For $1$-step ahead: $\left\{\overline{\mathcal{RL}}_{R+i|R+i-1}\right\}_{i=0}^{T-R-1}\!\!\!\!=\left\{\left(\overline{\eta}^{\alpha}_{R+i|R+i-1}\right)^{2}\!\!-\left(\overline{\eta}^{\gamma}_{R+i|R+i-1}\right)^{2}\right\}_{i=0}^{T-R-1}$
\item For $2$-step ahead: $\left\{\overline{\mathcal{RL}}_{R+i|R+i-2}\right\}_{i=0}^{T-R-2}\!\!\!\!=\left\{\left(\overline{\eta}^{\alpha}_{R+i|R+i-2}\right)^{2}\!\!-\left(\overline{\eta}^{\gamma}_{R+i|R+i-2}\right)^{2}\right\}_{i=0}^{T-R-2}$

@@

\item For $h$-step ahead: $\left\{\overline{\mathcal{RL}}_{R+i|R+i-h}\right\}_{i=0}^{T-R-h}\!\!\!\!=\left\{\left(\overline{\eta}^{\alpha}_{R+i|R+i-h}\right)^{2}\!\!-\left(\overline{\eta}^{\gamma}_{R+i|R+i-h}\right)^{2}\right\}_{i=0}^{T-R-h}$

@@

\item For the $1$-step ahead forecast regress $\left\{\overrightarrow{\mathcal{RL}}_{R+i+1|R+i}\right\}_{i=0}^{T-R-1}$ on $\left\{\overline{\mathcal{RL}}_{R+i|R+i-1}\right\}_{i=0}^{T-R-1}$.  The models being used to generate these losses are estimated on rolling windows that end on $R, R+1, \cdots, T$.
\item For the $2$-step ahead forecast regress $\left\{\overrightarrow{\mathcal{RL}}_{R+i+2|R+i}\right\}_{i=0}^{T-R-2}$ on $\left\{\overline{\mathcal{RL}}_{R+i|R+i-2}\right\}_{i=0}^{T-R-2}$.  The models being used to generate these losses are estimated on rolling windows that end on $R, R+1, \cdots, T$.

@@

\item For the $h$-step ahead forecast regress $\left\{\overrightarrow{\mathcal{RL}}_{R+i+h|R+i}\right\}_{i=0}^{T-R-h}$ on $\left\{\overline{\mathcal{RL}}_{R+i|R+i-h}\right\}_{i=0}^{T-R-h}$.  The models being used to generate these losses are estimated on rolling windows that end on $R, R+1, \cdots, T$.

@@

\item $1$-step: $\overrightarrow{\mathcal{RL}}_{R+i+1|R+i}=\widehat{\beta}_{1}\overline{\mathcal{RL}}_{R+i|R+i-1}+\widehat{u}_{R+i+1}$, where $i=0, 1, \cdots, T-R-1$.
\item $2$-step: $\overrightarrow{\mathcal{RL}}_{R+i+2|R+i}=\widehat{\beta}_{2}\overline{\mathcal{RL}}_{R+i|R+i-2}+\widehat{u}_{R+i+2}$, where $i=0, 1, \cdots, T-R-2$.

@@

\item $h$-step: $\overrightarrow{\mathcal{RL}}_{R+i+h|R+i}=\widehat{\beta}_{h}\overline{\mathcal{RL}}_{R+i|R+i-h}+\widehat{u}_{R+i+h}$, where $i=0, 1, \cdots, T-R-h$.
\item It may be worth noting that every out-of-sample-based loss being regressed on a corresponding in-sample-based loss uses exactly the same two versions -- where versions refer to the estimation period -- of the A and G model.  That is the models are all estimated on rolling windows ending $R, R+1, \cdots, T-s$ but the in-sample forecasts use this estimated model but condition on earlier data for period $R-s$, $R+1-s$, $\cdots$, $T-s-s$ (where $s=1,2,\cdots,h$) in generating the forecasts for periods $R, R+1, \cdots, T$ while the out-of-sample forecasts use this estimated model, condition on $R$, $R+1$, $\cdots$, $T-s$ data and project out  $R+s$, $R+1+s$, $\cdots$, $T$ (where $s=1,2,\cdots,h$).

@@

\item $1$-step: 

@@

\underbrace{\frac{1}{T\!-\!R}\!\!\sum_{i=0}^{T-R-1}\!\!\overrightarrow{\mathcal{RL}}_{R+i+1|R+i}}_{=A_{1,T-R}}
\!\!\!\!&=&\!\!\!\!\underbrace{\widehat{\beta}_{1}\cdot\frac{1}{T\!-\!R}\!\!\sum_{i=0}^{T-R-1}\!\!\overline{\mathcal{RL}}_{R+i|R+i-1}}_{=B_{1,T-R}} 
+\underbrace{\frac{1}{T\!-\!R}\!\!\sum_{i=0}^{T-R-1}\!\!\widehat{u}_{R+i+1}}_{=U_{1,T-R}}, \nonumber

@@

\item $2$-step: 

@@

\underbrace{\frac{1}{T\!-\!R\!-\!1}\!\!\sum_{i=0}^{T-R-2}\!\!\overrightarrow{\mathcal{RL}}_{R+i+2|R+i}}_{=A_{2,T-R-1}}
\!\!\!\!&=&\!\!\!\!\underbrace{\widehat{\beta}_{2}\cdot\frac{1}{T\!-\!R\!-\!1}\!\!\sum_{i=0}^{T-R-2}\!\!\overline{\mathcal{RL}}_{R+i|R+i-2}}_{=B_{2,T-R-1}} 
+\underbrace{\frac{1}{T\!-\!R\!-\!1}\!\!\sum_{i=0}^{T-R-2}\!\!\widehat{u}_{R+i+2}}_{=U_{2,T-R-1}}, \nonumber 

@@

@@

\item $h$-step: 

@@

\underbrace{\frac{1}{T\!-\!R\!-\!(h\!-\!1)}\!\!\!\!\sum_{i=0}^{T-R-h}\!\!\!\!\overrightarrow{\mathcal{RL}}_{R+i+h|R+i}}_{=A_{h,T-R-(h-1)}}
\!\!\!\!&=&\!\!\!\!\underbrace{\widehat{\beta}_{h}\cdot\frac{1}{T\!-\!R\!-\!(h\!-\!1)}\!\!\!\!\sum_{i=0}^{T-R-h}\!\!\!\!\overline{\mathcal{RL}}_{R+i|R+i-h}}_{=B_{h,T-R-(h-1)}} \ \ \ \   \ \ \ \    \ \ \ \   \ \ 
\nonumber \\
\!\!\!\!&+&\!\!\!\!
\underbrace{\frac{1}{T\!-\!R\!-\!(h\!-\!1)}\!\!\!\!\sum_{i=0}^{T-R-h}\!\!\!\!\widehat{u}_{R+i+h}}_{=U_{h,T-R-(h-1)}}, \nonumber

@@

@@

A_{h,T\!-\!R\!-\!\!(h\!-\!1)}\!\!\!\!&=&\!\!\!\!\frac{1}{T\!-\!R\!-\!(h\!-\!1)}\!\!\sum_{i=0}^{T-R-h}\!\!\overrightarrow{\mathcal{RL}}_{R+i+h|R+i}. \nonumber

@@

\item For $A_{1,T\!-\!R}$ there are $T-R-m+1$ possible windows, where the windows are: 
\[\left\{\overrightarrow{\mathcal{RL}}_{R+i+1+0|R+i+0}\ \ , \ \  . \ \  . \ \  . \ \ ,\ \ \overrightarrow{\mathcal{RL}}_{R+i+1+(m-1)|R+i+(m-1)}\right\}_{i=0}^{T-R-1+1-m}\] 

@@

\[\frac{1}{m}\sum_{j=0}^{m-1}\overrightarrow{\mathcal{RL}}_{R+i+1+j|R+i+j}\ \ \ \mathrm{for} \ \ \ i=0,1,\cdots,T\!-\!R\!-\!1\!+\!1\!-\!m. \]
\item For $A_{2,T\!-\!R\!-\!1}$ there are $T-R-m$ possible windows, where the windows are: 
\[\left\{\overrightarrow{\mathcal{RL}}_{R+i+2+0|R+i+0}\ \ , \ \  . \ \  . \ \  . \ \ ,\ \ \overrightarrow{\mathcal{RL}}_{R+i+2+(m-1)|R+i+(m-1)}\right\}_{i=0}^{T-R-2+1-m}\] 

@@

\[\frac{1}{m}\sum_{j=0}^{m-1}\overrightarrow{\mathcal{RL}}_{R+i+2+j|R+i+j}\ \ \ \mathrm{for} \ \ \ i=0,1,\cdots,T\!-\!R\!-\!2\!+\!1\!-\!m. \]

@@

\[\left\{\overrightarrow{\mathcal{RL}}_{R+i+h+0|R+i+0}\ \ , \ \  . \ \  . \ \  . \ \ ,\ \ \overrightarrow{\mathcal{RL}}_{R+i+h+(m-1)|R+i+(m-1)}\right\}_{i=0}^{T-R-h+1-m}\] 

@@

\[\frac{1}{m}\sum_{j=0}^{m-1}\overrightarrow{\mathcal{RL}}_{R+i+h+j|R+i+j}\ \ \ \mathrm{for} \ \ \ i=0,1,\cdots,T\!-\!R\!-\!h\!+\!1\!-\!m. \]

@@

\item The next step is to makes test statistics out of the $\left\{\left\{A_{i,s,T-R}\right\}_{i=0}^{T-R-s+1-m},B_{s,T-R},U_{s,T-R}\right\}_{s=1}^{h}$
